---
title: "Datawrangling_i_3"
author: "Lucia Wang"
date: "2023-09-26"
output: github_document
---

```{r}
library(tidyverse)

options(tibble.print_min=10)
```

## PULSE data
`Pivot_longer()` goes from wide to long
```{r}
pulse_df = 
  haven::read_sas("./data_import_examples/public_pulse_data.sas7bdat") |>
  janitor::clean_names() |>
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    values_to = "bdi_score",
    names_prefix = "bdi_score_"
  ) |>
  mutate(
    visit = replace(visit, visit == "bl", "00m")
  )

pulse_df
```
first you choose the variables to be pivoted with `:`, then name the new variable with `names_to`, then what values you want to use with `values_to`. finally, `names_prefix` gets rid of the prefix.

`replace()` takes in vector, logical statement, and replacement value

### learning assessment
```{r}
litters_df =
  read_csv("./data_import_examples/FAS_litters.csv") |>
  janitor::clean_names() |>
  select(litter_number, gd0_weight, gd18_weight) |>
  pivot_longer(
    gd0_weight:gd18_weight, 
    names_to = "gd",
    values_to = "weight"
  ) |>
  mutate(
    gd = case_match(
      gd, 
      "gd0_weight"  ~ 0,
      "gd18_weight" ~ 18
    )
  )
  
litters_df
```

`case_match` helps you replace a bunch of stuff using the `~` 
  

