---
title: "P8105 - Data Wrangling I"
output: github_document
---

```{r}
library(tidyverse)
```

### Notes

* put data and code in same project because otherwise it might get tricky due to different paths 

* relative paths - starting from where you are (project/directory)
absolute - full address on your computer

* by default, `read_csv` thinks the first row is column names 

# Class practice
Import `FAS_litters.csv` and clean up variable names (convert to lowercase and add underscores). We want to use `janitor` package but not load it so we use `package :: function` syntax just for that.

```{r}
litters_df =
  read_csv(file="data_import_examples/FAS_litters.csv")

litters_df = 
  janitor ::clean_names(litters_df)
```

Now using absolute path...
```{r}
litters_df_abs =
  read_csv(file="C:/Users/wangl/OneDrive - cumc.columbia.edu/Data Science/Class/datawrangling_i/data_import_examples/FAS_litters.csv")

litters_df_abs = 
  janitor ::clean_names(litters_df_abs)
```

Now importing pups_data
```{r}
pups_df = read_csv(file="data_import_examples/FAS_pups.csv")

pups_df = janitor :: clean_names(pups_df)
```

## Look at data
print your df using its name, or use `head()`- prints first 6 rows, `tail()`- the last 6
```{r}
litters_df

head(litters_df)

tail(litters_df)
```
or  `view()`- see it in another window (don't include in Rmd file)
```{r, eval=FALSE}
view(litters_df)
```

data summary code
```{r}
str(litters_df)

skimr::skim(litters_df)
```

## Options in `read_*`
you can skip rows in `read_csv` but might run into some issues
```{r}
litters_df = 
  read_csv("data_import_examples/FAS_litters.csv", skip=10)
```

missing data is "NA" in the file, but it can be changed to a string or you can choose what values to code as NA
```{r}
litters_df = 
  read_csv("data_import_examples/FAS_litters.csv", na=c('NA',19,"."))
```

`readr` does column parsing to figure out variable types by looking at first 1000 rows. you can be explicit in what type it is or tell R to read more rows. (here, we made the Group variable a factor variable)
```{r}
litters_df = 
  read_csv("data_import_examples/FAS_litters.csv", 
           col_types = 
             cols(
               Group= col_factor()
             ))
```

## Other file types
import xlsx
```{r}

```

