---
title: "P8105 - Data Wrangling I"
output: github_document
---

```{r}
library(tidyverse)
```

### Notes
put data and code in same project because otherwise it might get tricky due to different paths 

relative paths - starting from where you are (project/directory)
absolute - full address on your computer

# Class practice
Import `FAS_litters.csv` and clean up variable names (convert to lowercase and add underscores). We want to use `janitor` package but not load it so we use `package :: function` syntax just for that.

```{r}
litters_df =
  read_csv(file="data_import_examples/FAS_litters.csv")

litters_df = 
  janitor ::clean_names(litters_df)
```

Now using absolute path...
```{r}
litters_df_abs =
  read_csv(file="C:/Users/wangl/OneDrive - cumc.columbia.edu/Data Science/Class/datawrangling_i/data_import_examples/FAS_litters.csv")

litters_df_abs = 
  janitor ::clean_names(litters_df_abs)
```

Now importing pups_data
```{r}
pups_df = read_csv(file="data_import_examples/FAS_pups.csv")

pups_df = janitor :: clean_names(pups_df)
```

## Look at data
print your df using its name, or use `head()`- prints first 6 rows, `tail()`- the last 6
```{r}
litters_df

head(litters_df)

tail(litters_df)
```
or  `view()`- see it in another window (don't include in Rmd file)
```{r, eval=FALSE}
view(litters_df)
```

data summary code
```{r}
str(litters_df)

skimr::skim(litters_df)
```


