---
title: "Datawrangling_i_3"
author: "Lucia Wang"
date: "2023-09-26"
output: github_document
---

```{r}
library(tidyverse)

options(tibble.print_min=10)
```

## PULSE data
`Pivot_longer()` goes from wide to long
```{r}
pulse_df = 
  haven::read_sas("./data_import_examples/public_pulse_data.sas7bdat") |>
  janitor::clean_names() |>
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    values_to = "bdi_score",
    names_prefix = "bdi_score_"
  ) |>
  mutate(
    visit = replace(visit, visit == "bl", "00m")
  )

pulse_df
```
first you choose the variables to be pivoted with `:`, then name the new variable with `names_to`, then what values you want to use with `values_to`. finally, `names_prefix` gets rid of the prefix.

`replace()` takes in vector, logical statement, and replacement value

### learning assessment
```{r}
litters_df =
  read_csv("./data_import_examples/FAS_litters.csv") |>
  janitor::clean_names() |>
  select(litter_number, gd0_weight, gd18_weight) |>
  pivot_longer(
    gd0_weight:gd18_weight, 
    names_to = "gd",
    values_to = "weight"
  ) |>
  mutate(
    gd = case_match(
      gd, 
      "gd0_weight"  ~ 0,
      "gd18_weight" ~ 18
    )
  )
  
litters_df
```

`case_match` helps you replace a bunch of stuff using the `~` 
  
## LOTR - bind rows
Import LOTR words data, from 3 tables. `bind_rows()` stacks them together
```{r}
fellowship_df = 
  readxl::read_excel("./data_import_examples/LotR_Words.xlsx", range="B3:D6") |>
  mutate(movie = "fellowship")

twotowers_df = 
  readxl::read_excel("./data_import_examples/LotR_Words.xlsx", range="F3:H6") |>
  mutate(movie = "two towers")

returnoftheking_df = 
  readxl::read_excel("./data_import_examples/LotR_Words.xlsx", range="J3:L6") |>
  mutate(movie = "return of the king")

lotr_df =
  bind_rows(
    fellowship_df, twotowers_df, returnoftheking_df
  ) |>
  pivot_longer(
    Male:Female,
    names_to = "gender",
    values_to = "word"
  ) |>
  relocate(movie)

```

## Revisit FAS

```{r}
litters_df = 
  read_csv("data_import_examples/FAS_litters.csv") |>
  janitor::clean_names() |>
  mutate(wt_gain = gd18_weight - gd0_weight) |>
  select(litter_number, group, wt_gain) |>
  separate(group, into = c("dose", "day_of_tx"), 3)

litters_df

pups_df =
  read_csv("data_import_examples/FAS_pups.csv") |>
  janitor::clean_names() |> 
  mutate(
    sex = case_match(
      sex,
      1 ~ "male",
      2 ~ "female"
    )
  )

pups_df

fas_df = 
  left_join(pups_df, litters_df, by = "litter_number")

fas_df
```
`separate` can split a variable into two - be careful where you want to split it.

`left_join` used here to bring litters into pups data. use the key `by` or it will look for columns with same name by default




